MOM PS Estimator under Strong Monotonicity

### 2021-04-30 Mest.tex
took out estimated principal scores from writeup--math was wrong

@@

For subject $i$, $i=1,\dots,n$, we have:
\begin{itemize}
\item $Y_i$ observed outcome
\item $S_i \in \{0,1\}$ unobserved stratum
\item $\ppi=Pr(S_i=1|\bm{X}_i)$ %take as given (like, estimated from
  % treatment group)
\item $\hppi$ is an estimate of $\ppi$ from a separate sample
  (treatment group?) with $\EE[\hppi|\ppi]=\ppi$
\end{itemize}

@@

\section{M-Estimator}
As a preliminary, note that
\begin{align*}
  \EE[S|\hpp]&=\EE\left\{\EE[S|\pp,\hpp]|\hpp\right\}\\
             &=\EE\left\{\EE[S|\pp]|\hpp\right\}\\
             &=\EE[\pp|\hpp]=\hpp
\end{align*}

Then, note
\begin{align*}
  \EE[Y|\hpp]&=\EE\left\{\EE[Y|\hpp,S]|\hpp\right\}\\
             &=\EE\left\{\EE[Y|S]|\hpp\right\}\\
             &=\EE[\mu_1S+\mu_0(1-S)|\hpp]\\
             &=\mu_1\hpp+\mu_0(1-\hpp)
\end{align*}

Then we have
\begin{equation*}
  \EE[Y]=\EE\EE[Y|\hpp]=\mu_1\EE\hpp+\mu_0(1-\EE\hpp)
\end{equation*}

@@

\begin{align*}
  \EE[Y\hpp]&=\EE\left\{\EE[Y\hpp|\hpp]\right\}\\
            &=\EE\left\{\hpp\EE[Y|\hpp]\right\}\\
            &=\EE\left\{\hpp\left[\mu_1\hpp+\mu_0(1-\hpp)\right]\right\}\\
            &=\mu_1\EE[\hpp^2]+\mu_0\left(\EE[\hpp]-\EE[\hpp^2]\right)
\end{align*}

That gives us four parameters:
\begin{align*}
  \theta_1&=\EE[\hpp]\\
  \theta_2&=\EE[\hpp^2]\\
  \theta_3&=\mu_0\\
  \theta_4&=\mu_1
\end{align*}

and four estimating equations:
\begin{align*}
  \sum_i \hppi-\theta_1&=0\\
  \sum_i \hppi^2-\theta_2&=0\\
  \sum_i Y_i-\theta_4\theta_1-\theta_3(1-\theta_1)&=0\\
  \sum_i Y_i\hppi-\theta_4\theta_2-\theta_3(\theta_1-\theta_2)&=0
\end{align*}

@@

But say you believe the model
\begin{equation}\label{eq:regression}
Y_i=\bm{x}_i'\bm{\beta}+\gamma S_i+\epsilon_i
\end{equation}
 Then instead of \eqref{eq:assumption} we could assume something like
\begin{equation*}
\EE[Y_i-\bm{x}_i'\bm{\beta}|\bm{X}_i,S_i]=\EE[Y_i-\bm{x}_i'\bm{\beta}|S_i]
\end{equation*}

>>>>

[NOTE: I updated this taking **out** references to \emph{estimated}
principal scores, cuz I realized the math was wrong. I'm following the
propensity score literature and ignoring estimation error, for the moment]\\

@@

For subject $i$, $i=1,\dots,n$, we have:
\begin{itemize}
\item $Y_i$ observed outcome
\item $S_i \in \{0,1\}$ unobserved stratum
\item $\ppi=Pr(S_i=1|\bm{X}_i)$ take as given (like, estimated from
  % treatment group)
%\item $\hppi$ is an estimate of $\ppi$ from a separate sample
%  (treatment group?) with $\EE[\hppi|\ppi]=\ppi$
\end{itemize}

@@

\section{M-Estimator}
As a preliminary, note that
% \begin{align*}
%   \EE[S|\hpp]&=\EE\left\{\EE[S|\pp,\hpp]|\hpp\right\}\\
%              &=\EE\left\{\EE[S|\pp]|\hpp\right\}\\
%              &=\EE[\pp|\hpp]=\hpp
% \end{align*}

%Then, note
\begin{align*}
  \EE[Y|\pp]&=\EE\left\{\EE[Y|\pp,S]|\pp\right\}\\
             &=\EE\left\{\EE[Y|S]|\pp\right\}\text{ by \eqref{eq:assumption}}\\
             &=\EE[\mu_1S+\mu_0(1-S)|\pp]\\
             &=\mu_1\pp+\mu_0(1-\pp)
\end{align*}

Then we have
\begin{equation*}
  \EE[Y]=\EE\EE[Y|\pp]=\mu_1\EE\pp+\mu_0(1-\EE\pp)
\end{equation*}

@@

\begin{align*}
  \EE[Y\pp]&=\EE\left\{\EE[Y\pp|\pp]\right\}\\
            &=\EE\left\{\pp\EE[Y|\pp]\right\}\\
            &=\EE\left\{\pp\left[\mu_1\pp+\mu_0(1-\pp)\right]\right\}\\
            &=\mu_1\EE[\pp^2]+\mu_0\left(\EE[\pp]-\EE[\pp^2]\right)
\end{align*}

That gives us four parameters:
\begin{align*}
  \theta_1&=\EE[\pp]\\
  \theta_2&=\EE[\pp^2]\\
  \theta_3&=\mu_0\\
  \theta_4&=\mu_1
\end{align*}

and four estimating equations:
\begin{align*}
  \sum_i \ppi-\theta_1&=0\\
  \sum_i \ppi^2-\theta_2&=0\\
  \sum_i Y_i-\theta_4\theta_1-\theta_3(1-\theta_1)&=0\\
  \sum_i Y_i\ppi-\theta_4\theta_2-\theta_3(\theta_1-\theta_2)&=0
\end{align*}

@@

But say you believe the model
\begin{equation}\label{eq:regression}
Y_i=\mu_1S_i+\mu_0(1-S_i)+\bm{x}_i'\bm{\beta}+\epsilon_i
\end{equation}
 Then instead of \eqref{eq:assumption} we could assume something like
\begin{equation*}
\EE[Y_i-\bm{x}_i'\bm{\beta}|\bm{X}_i,S_i]=\EE[Y_i-\bm{x}_i'\bm{\beta}|S_i]
\end{equation*}

Under model \eqref{eq:regression}, we have new estimating equations.

\begin{align*}
  \EE[Y]&=\EE\left[\mu_1\pp+\mu_0(1-\pp)+\bm{X}\bm{\beta}\right]\\
  \EE[Y\pp]&=\EE\left[\pp\left(\mu_1\pp+\mu_0(1-\pp)+\bm{X}\bm{\beta}\right)\right]\\
  \EE[\bm{X}Y]&\EE\left[\bm{X}\left(\mu_1\pp+\mu_0(1-\pp)+\bm{X}\bm{\beta}\right)\right]\\
\end{align*}
